Shannon-Inspired Information in the Clinical Use of Neural Signals Concerning Post-Comatose Patients

### 2023-02-06 ART_Martin/Martin.tex
Final commit before sending to the editors for corrections

\begin{artengenv2auth}{Alice Martin, Mathieu Magnaudet, Stéphane Conversy}
	{Modelling interactive computing systems: Do we have a~good theory of what computers are?}
	{Modelling interactive computing systems\ldots}
	{Modelling interactive computing systems: Do we have a~good theory\\of what computers are?}
	{\textsuperscript{1}Departments of Philosophy and Mathematics, Carnegie Mellon University\\
		\textsuperscript{2}Copernicus Center for Interdisciplinary Studies, Jagiellonian University}
	{Computers are increasingly interactive. They are no more transformational systems producing a~final output after a~finite execution. Instead, they continuously react in time to external events that modify the course of computing execution. While philosophers have been interested in conceptualizing computers for a~long time, they seem to have paid little attention to the specificities of interactive computing. We propose to tackle this issue by surveying the literature in theoretical computer science, where one can find explicit proposals for a~model of interactive computing. 
	In that field, the formal modelling of interactive computing systems has been brought down to whether the new interaction models are reducible to Turing Machines. There are three areas where interaction models are framed. The comparison between TMs and interactive system models is at stake in all of them. These areas are namely some works on concurrency by Milner, on Reactive Turing Machines, and on interaction as a~new computing paradigm. For each of the three identified models, we present its motivation, sum up its account for interaction and its legacy, and point out issues regarding the understanding of computers. The survey shows difficulties for epistemologists. The reason is that these analyses focus on the formal equivalence between interactive models of computation and classic ones. Such a~project is different from addressing how a~computing machine can be interactive: in other words, which mechanisms allow it.}
	{philosophy of computing, models of computation, interactive computing, computing mechanism, computational mechanistic explanation.}
	{%
		{\flushright\subbold{Alice Martin}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
		{\flushright\subbold{Mathieu Magnaudet}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
		{\flushright\subbold{Stéphane Conversy}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
	}

@@

In the philosophy of computing, we are paying increased attention to a~set of new features of computers. This set has led to the introduction of a~new label for these computing machines: they are referred to as interactive computing machines \parencite{Dodig-Crnkovic2011, Goldin2006, Soare2013, VanLeeuwen2001, Wegner1997}. The set of new features can be captured in the following statement made in a~2011 paper by Gordana Dodig-Crnkovic (our highlights):

>>>>

\begin{artengenv2auth}{Alice Martin, Mathieu Magnaudet, Stéphane Conversy}
	{Modelling interactive computing systems: Do we have a~good theory of what computers are?}
	{Modelling interactive computing systems\ldots}
	{Modelling interactive computing systems: Do we have a~good theory\\of what computers are?}
	{\textsuperscript{1}Departments of Philosophy and Mathematics, Carnegie Mellon University\\
		\textsuperscript{2}Copernicus Center for Interdisciplinary Studies, Jagiellonian University}
	{Computers are increasingly interactive. They are no more transformational systems producing a~final output after a~finite execution. Instead, they continuously react in time to external events that modify the course of computing execution. While philosophers have been interested in conceptualizing computers for a~long time, they seem to have paid little attention to the specificities of interactive computing. We propose to tackle this issue by surveying the literature in theoretical computer science, where one can find explicit proposals for a~model of interactive computing. 
	In that field, the formal modelling of interactive computing systems has been brought down to whether the new interaction models are reducible to Turing Machines. There are three areas where interaction models are framed. The comparison between TMs and interactive system models is at stake in all of them. These areas are namely some works on concurrency by Milner, on Reactive Turing Machines, and on interaction as a~new computing paradigm. For each of the three identified models, we present its motivation, sum up its account for interaction and its legacy, and point out issues regarding the understanding of computers. The survey shows difficulties for epistemologists. The reason is that these analyses focus on the formal equivalence between interactive models of computation and classic ones. Such a~project is different from addressing how a~computing machine can be interactive: in other words, which mechanisms allow it.}
	{philosophy of computing, models of computation, interactive computing, computing mechanism, computational mechanistic explanation.}
	{%
%		{\flushright\subbold{Alice Martin}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
%		{\flushright\subbold{Mathieu Magnaudet}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
%		{\flushright\subbold{Stéphane Conversy}\\\subsubsectit\small{ENAC, Université de Toulouse}\par}%
				{\flushright\subbold{Alice Martin}\\\subbold{Mathieu Magnaudet}\\\subbold{Stéphane Conversy}\\
				\subsubsectit\small{ENAC, Université de Toulouse}\par}%
	}

@@

\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{I}{}n the philosophy of computing, we are paying increased attention to a~set of new features of computers. This set has led to the introduction of a~new label for these computing machines: they are referred to as interactive computing machines \parencite{Dodig-Crnkovic2011, Goldin2006, Soare2013, VanLeeuwen2001, Wegner1997}. The set of new features can be captured in the following statement made in a~2011 paper by Gordana Dodig-Crnkovic (our highlights):

### 2023-02-06 ART_Mscislawski/Mscislaw.tex
Final commit before sending to the editors for corrections

\begin{artengenv}{Łukasz Mścisławski}
	{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
	{Is information ontological or physical, or is it perhaps\ldots}
	{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
	{Wrocław University of Science and Technology}
	{As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
	%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
	\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
	 proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
	%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
	\parencite[][]{ellis_space_2012}. %
	 This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.
	}
	{physical information, ontology, physics, philosophy of information.}

%\begin{document}
%\title{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
%\maketitle
%
%Łukasz Mścisławski
%
%Politechnika Wrocławska
%
%\url{https://orcid.org/0000-0003-0195-906}
%
%\section{Abstract}
%As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
%%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
%\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
% proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
%%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
%\parencite[][]{ellis_space_2012}. %
% This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.

\section{Introduction}
This article primarily aims to concisely present Roman Krzanowski's approach to the concept of \textit{physical information.} This concept is perceived here as a~kind of ``intermediate concept'' that can act as a~bridge to the development of his concept of \textit{ontological information}
%\label{ref:RNDVGZ8jlBX2V}(cf. Krzanowski, 2020a; 2020b; 2020c; 2022),
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[and especially][]{krzanowski_ontological_2022},%
and can be regarded as a~special case of the latter. Indeed, we believe that the latter concept inherits many characteristics from the former, but not all the issues have been solved.\footnote{It is also worth mentioning that in some works, Krzanowski seems to use these two terms (i.e., physical and ontological information) interchangeably
%\label{ref:RNDx2sgo6ehaO}(cf. Krzanowski, 2020b).
\parencite[cf.][]{krzanowski_what_2020}.%
} This situation implies that we are dealing with a~truly fundamental issue here, namely the fundamentality of the concept of information. Furthermore, this paper also aims to discuss some of this concept's interesting properties and present possible avenues for further developing this interesting proposal. It is well known that there is enormous interest in the philosophical aspects of the concept of information 
%\label{ref:RNDKUzkfsqSdA}(e.g. Adriaans and Benthem, 2008; Burgin, 2010; Floridi, 2011; Dodig Crnkovic and Burgin, 2019),
\parencites[e.g.,][]{adriaans_philosophy_2008}[][]{burgin_theory_2010}[][]{floridi_philosophy_2011}[][]{dodig_crnkovic_philosophy_2019}, %
 but we feel that Krzanowski's proposal is particularly attractive with some great research potential, especially for studying physical reality. It would %
therefore be helpful, in our opinion, to position this concept within the vast array of philosophical problems related to the notion of information, as well as introduce a~few distinctions to allow us to order the discourse.

@@

\section{The concept of physical information}

@@

\section{Remarks and potential avenues for further development}

@@

\section{Conclusion}
We find Krzanowski's proposed concept of physical information very interesting, particularly at a~certain stage in his study of the concept of information. While there are many points in which this concept seems to be ambiguous, there are also some interesting areas for possible further research. Thus, we have endeavoured to present the concept and point out the problematic aspects. Most of these could be regarded as potential starting points for further study, despite the fact that some of these ambiguities were partially clarified in the concept of ontological information presented by Krzanowski
%\label{ref:RNDgvjMJHNDo8}(2022).
\parencite*[][]{krzanowski_ontological_2022}. %
 Nevertheless, presenting this concept in light of the issues presented above warrants a~separate study.

@@

\end{artengenv}

%\section{Bibliography}
%Adriaans, P. and Benthem, J. van, 2008. \textit{Philosophy of information}. Amsterdam, The Netherlands; Boston: North Holland.
%
%Białobrzeski, C., 1984. Podstawy poznawcze fizyki świata atomowego. In: \textit{Podstawy poznawcze fizyki świata atomowego}, Wyd. 2 rozszerzone. Warszawa: Państwowe Wydawnictwo Naukowe. pp.19–288.
%
%Burgin, M., 2010. \textit{Theory of information: fundamentality, diversity and unification}. World Scientific series in information studies. Hackensack, NJ: World Scientific Pub Co Inc.
%
%Burgin, M., 2011. Information: Concept Clarification and Theoretical Representation. \textit{tripleC: Communication, Capitalism \& Critique. Open Access Journal for a~Global Sustainable Information Society}, [online] 9(2), pp.347–357. https://doi.org/10.31269/triplec.v9i2.284.
%
%Burgin, M., 2017. The General Theory of Information as a~Unifying Factor for Information Studies: The Noble Eight-Fold Path. \textit{Proceedings}, [online] 1(3), p.164. https://doi.org/10.3390/IS4SI-2017-04044.
%
%Davies, 2020. \textit{The demon in the machine: how hidden webs of information are solving the mystery of life}. London: Penguin Books.
%
%Davies, P.C.W., 2007. The Implications of a~Cosmological Information Bound for Complexity, Quantum Information and the Nature of Physical Law. In: C. Claude and G.J. Chaitin, eds. \textit{Randomness and Complexity, From Leibniz to Chaitin}. World Scientific. pp.69–87.
%
%Dodig Crnkovic, G. and Burgin, M.S. eds., 2019. \textit{Philosophy and methodology of information: the study of information in a~transdisciplinary perspective}. World scientific series in information studies. New Jersey: World Scientific.
%
%Dodig-Crnkovic, G., 2013. Alan Turing's Legacy: Info-computational Philosophy of Nature. In: G. Dodig-Crnkovic and R. Giovagnoli, eds. \textit{Computing Nature: Turing Centenary Perspective}, Studies in Applied Philosophy, Epistemology and Rational Ethics. Berlin, Heidelberg: Springer. pp.115–123. https://doi.org/10.1007/978-3-642-37225-4\_6.
%
%Ellis, G.F.R. and Goswami, R., 2012. Space time and the passage of time. \textit{arXiv:1208.2611 [gr-qc}]. [online] Available at: {\textless}http://arxiv.org/abs/1208.2611{\textgreater} [Accessed 10 June 2014].
%
%Floridi, L., 2011. \textit{The philosophy of information}. Oxford: Oxford University Press.
%
%Grygiel, W.P., 2022. A~critical analysis of the philosophical motivations and development of the concept of the field of rationality as a~representation of the fundamental ontology of the physical reality. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), (72), pp.87–108.
%
%Hawking, S., 1988. \textit{A~brief history of time: from the big bang to black holes.} New York, Toronto: Bantam Books.
%
%Heller, M., 1998. Czy świat jest matematyczny? \textit{Zagadnienia Filozoficzne w~Nauce}, 23, pp.3–14.
%
%Heller, M., 2014. \textit{Elementy mechaniki kwantowej dla filozofów}. Wyd. 1 w~tej edycji ed. Kraków: Copernicus Center Press.
%
%Krzanowski, R., 2020a. Does purely physical information have meaning? A~comment on Carlo Rovelli's paper: Meaning = information + evolution. \textit{arXiv:2004.06716 [physics}]. [online] Available at: {\textless}http://arxiv.org/abs/2004.06716{\textgreater} [Accessed 30 November 2021].
%
%Krzanowski, R., 2020b. What Is Physical Information? \textit{Philosophies}, [online] 5(2), pp.9–22. https://doi.org/10.3390/philosophies5020010.
%
%Krzanowski, R., 2020c. Why can information not be defined as being purely epistemic? \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), [online] (68), pp.37–62. Available at: {\textless}https://zfn.edu.pl/index.php/zfn/article/view/494{\textgreater} [Accessed 30 November 2021].
%
%Krzanowski, R., 2022. \textit{Ontological information: information in the physical world}. Hackensack, New Jersey: World Scientific.
%
%Mścisławski, Ł., 2017. Między filozofią w~nauce a~filozofią przyrody: piękno systemu w~konkrecie: zakaz Pauliego a~filozofia Czesława Białobrzeskiego. In: P. Polak, J. Mączka and W.P. Grygiel, eds. \textit{Oblicza filozofii w~nauce: księga pamiątkowa z~okazji 80. urodzin Michała Hellera}. Kraków: Copernicus Center Press. pp.133–153.
%
%Nagel, T., 2012. \textit{Mind and cosmos: why the materialist neo-Darwinian conception of nature is almost certainly false}. New York: Oxford University Press.
%
%Penrose, R., 2006. \textit{The road to reality: a~complete guide to the laws of the universe}. 6th print. ed. New York: Alfred AKnopf.
%
%Perzanowski, J.W., 2015. \textit{Rozprawa ontologiczna i~inne eseje}. Toruń: Wydawnictwo Adam Marszałek.
%
%Rovelli, C., 2016. Meaning = Information + Evolution. \textit{arXiv:1611.02420 [physics}]. [online] Available at: {\textless}http://arxiv.org/abs/1611.02420{\textgreater} [Accessed 15 December 2021].
%
%Skowron, B., 2020. Virtual objects: Becoming real. \textit{Horizon, Fenomenologiceskie Issledovania}, [online] 9(2). https://doi.org/10.21638/2226-5260-2020-9-2-619-639.
%
%Turek, K., 1978. Filozoficzne aspekty pojęcia informacji. \textit{Philosophical Problems in Science (Zagadnienia Filozoficzne w~Nauce}), (1), pp.32–41.
%
%von Weizsäcker, C.F., 1982. \textit{Die Einheit der Natur}. München: Deutscher Taschenbuch Verlag.
%
%Wilczek, F., 2016. \textit{A~beautiful question: finding nature's deep design}. London.
%
%Zurek, W.H., 2002. Decoherence and the Transition from Quantum to Classical — Revisited. \textit{Los Alamos Science}, [online] (27), pp.2–25. https://doi.org/10.1007/978-3-7643-7808-0\_1.
%\end{document}

>>>>

\begin{artengenv}{Łukasz Mścisławski}
	{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
	{Is information ontological or physical, or is it perhaps\ldots}
	{Is information ontological or physical, or is it perhaps something\\else? Some remarks on Krzanowski's approach to the concept of\\information}
	{Wrocław University of Science and Technology}
	{\label{mscislaw_start}As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
	%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
	\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
	 proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
	%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
	\parencite[][]{ellis_space_2012}. %
	 This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.
	}
	{physical information, ontology, physics, philosophy of information.}

%\begin{document}
%\title{Is information ontological or physical, or is it perhaps something else? Some remarks on Krzanowski's approach to the concept of information}
%\maketitle
%
%Łukasz Mścisławski
%
%Politechnika Wrocławska
%
%\url{https://orcid.org/0000-0003-0195-906}
%
%\section*{Abstract}
%As one may have noticed, the title of this paper is somewhat provocative. We found Roman Krzanowski's
%%\label{ref:RNDD4ZPbWpWxt}(2020a; 2020b; 2020c; 2022)
%\parencites*[][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[][]{krzanowski_ontological_2022} %
% proposed approach to the problem of information very intriguing. Our aim here is to highlight some advantages when it comes to answering some fundamental questions in the philosophy of physics and metaphysics, as well as the philosophy of information and computer science. This issue is of great importance, so we propose that the introduction of some subtle distinctions between ontological and epistemological information can be regarded as being analogous to G.F.R. Ellis's analyses of the passage of time in his concept of the Crystallizing Block Universe 
%%\label{ref:RNDaS7kEBPadF}(Ellis and Goswami, 2012).
%\parencite[][]{ellis_space_2012}. %
% This analogy could be useful when further studying the relations between different types of information. We also suggest some subjects for further study, ones where Krzanowski's proposal could serve as a~very solid foundation for examining traditional metaphysical issues by combining classical philosophical doctrines with the new approach.

\section*{Introduction}
\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{T}{}his article primarily aims to concisely present Roman Krzanowski's approach to the concept of \textit{physical information.} This concept is perceived here as a~kind of ``intermediate concept'' that can act as a~bridge to the development of his concept of \textit{ontological information}
%\label{ref:RNDVGZ8jlBX2V}(cf. Krzanowski, 2020a; 2020b; 2020c; 2022),
\parencites[cf.][]{krzanowski_does_2020}[][]{krzanowski_what_2020}[][]{krzanowski_why_2020}[and especially][]{krzanowski_ontological_2022},%
and can be regarded as a~special case of the latter. Indeed, we believe that the latter concept inherits many characteristics from the former, but not all the issues have been solved.\footnote{It is also worth mentioning that in some works, Krzanowski seems to use these two terms (i.e., physical and ontological information) interchangeably
%\label{ref:RNDx2sgo6ehaO}(cf. Krzanowski, 2020b).
\parencite[cf.][]{krzanowski_what_2020}.%
} This situation implies that we are dealing with a~truly fundamental issue here, namely the fundamentality of the concept of information. Furthermore, this paper also aims to discuss some of this concept's interesting properties and present possible avenues for further developing this interesting proposal. It is well known that there is enormous interest in the philosophical aspects of the concept of information 
%\label{ref:RNDKUzkfsqSdA}(e.g. Adriaans and Benthem, 2008; Burgin, 2010; Floridi, 2011; Dodig Crnkovic and Burgin, 2019),
\parencites[e.g.,][]{adriaans_philosophy_2008}[][]{burgin_theory_2010}[][]{floridi_philosophy_2011}[][]{dodig_crnkovic_philosophy_2019}, %
 but we feel that Krzanowski's proposal is particularly attractive with some great research potential, especially for studying physical reality. It would %
therefore be helpful, in our opinion, to position this concept within the vast array of philosophical problems related to the notion of information, as well as introduce a~few distinctions to allow us to order the discourse.

@@

\section*{The concept of physical information}

@@

\section*{Remarks and potential avenues for further development}

@@

\section*{Conclusion}
We find Krzanowski's proposed concept of physical information very interesting, particularly at a~certain stage in his study of the concept of information. While there are many points in which this concept seems to be ambiguous, there are also some interesting areas for possible further research. Thus, we have endeavoured to present the concept and point out the problematic aspects. Most of these could be regarded as potential starting points for further study, despite the fact that some of these ambiguities were partially clarified in the concept of ontological information presented by Krzanowski
%\label{ref:RNDgvjMJHNDo8}(2022).
\parencite*[][]{krzanowski_ontological_2022}. %
 Nevertheless, presenting this concept in light of the issues presented above warrants a~separate study.

@@

\end{artengenv}
\label{mscislaw_stop}

### 2023-02-06 ART_Noh/Noh.tex
Soloducha article added
Final commit before sending to the editors for corrections

\begin{artengenv}{Hyungrae Noh}
	{Shannon-inspired information in the clinical use of neural signals concerning post-comatose patients}
	{Shannon-inspired information in the clinical use of neural signals\ldots}
	{Shannon-inspired information in the clinical use of neural signals concerning post-comatose patients}
	{Sunchon National Unviersity}
	{Post-comatose patients are classified as being in a~minimally conscious state when they have executive functions. Because traditional behavioral assessments may not capture signs of executive functions in post-comatose patients, clinicians look to localized brain activities in response to task instructions, such as imagining wiggling toes, to diagnose minimal consciousness. This paper critically assesses the assumption underlying such alternative methods: that brain activities are neural signals conveying information about minimal consciousness. Based on a~Shannon-inspired idea of information, I~distinguish between informational and engineering aspects of clinical tasks. The informational aspect concerns the conditional probability that, for example, given activity in the motor areas of the brain in response to task instructions, a~patient is imagining wiggling toes. The engineering aspect concerns efficient activation of the relevant brain areas in a~patient under the task conditions. This distinction shows that the current alternative methods are not informationally problematic, but are structurally ``ill-formed.'' For instance, the toe-imagery task requires the capacity to comprehend syntactically complex sentences, which can be dissociated from minimal consciousness. I~propose a~misrepresentation task, which tests the capacity to misconceptualize lukewarm water as melting wax, as a~supplement to the current alternative methods. This task is as informationally reliable as these methods, but is structurally ``well-formed,'' as it does not rely methodologically on prerequisites such as language comprehension.
	}
	{post-comatose disorders of consciousness, Shannon's theory of information, minimal consciousness, mental action.}

\section{Introduction}
Minimally conscious post-comatose patients (henceforth, MCP patients) can have limited executive functions that allow for the patients to follow simple instructions or respond to certain stimulations. Signs of residual executive functions provide clinicians with strong evidence of eventual recovery of consciousness
%\label{ref:RNDc52VR2C0H1}(Naccache, 2018; Rohaut, Eliseyev and Claassen, 2019).
\parencites[][]{naccache_minimally_2018}[][]{rohaut_uncovering_2019}. %
 Thus, delayed recognition of such signs may lead to suboptimal clinical care 
%\label{ref:RND36iYhUl47e}(van Erp et al., 2019),
\parencite[van][]{van_erp_unexpected_2019}, %
 distorted prognostic figures for rehabilitation 
%\label{ref:RNDDiumYQqtvx}(Ansell, 1993),
\parencite[][]{ansell_slow--recover_1993}, %
 or ethical problems 
%\label{ref:RNDY4B7wdnTLX}(Peterson and Bayne, 2018; Noh, 2022).
\parencites[][]{peterson_post-comatose_2018}[][]{noh_behavioral_2022}. %
 Such signs, however, might not be captured by traditional behavioral assessments (e.g., eye tracking, speaking, etc.) because limited executive functions can be dissociated from the capacity to perform overt behaviors 
%\label{ref:RND1VSfdAw16s}(Teasdale and Jennett, 1974; Andrews et al., 1996).
\parencites[][]{teasdale_assessment_1974}[][]{andrews_misdiagnosis_1996}. %
 Although some traditional behavioral assessment methods can improve diagnostic accuracy 
%\label{ref:RNDkWoQFW7Rb7}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 differentiating MCP patients from patients in a~vegetative state remains challenging 
%\label{ref:RNDXmlWJMWjeY}(van Erp et al., 2015).
\parencite[van][]{van_erp_vegetative_2015}.%

>>>>

\begin{artengenv}{Hyungrae Noh}
	{Shannon-inspired information in the clinical use of neural signals concerning post-comatose patients}
	{Shannon-inspired information in the clinical use of neural signals\ldots}
	{Shannon-inspired information in the clinical use of neural signals\\concerning post-comatose patients}
	{Sunchon National Unviersity}
	{Post-comatose patients are classified as being in a~minimally conscious state when they have executive functions. Because traditional behavioral assessments may not capture signs of executive functions in post-comatose patients, clinicians look to localized brain activities in response to task instructions, such as imagining wiggling toes, to diagnose minimal consciousness. This paper critically assesses the assumption underlying such alternative methods: that brain activities are neural signals conveying information about minimal consciousness. Based on a~Shannon-inspired idea of information, I~distinguish between informational and engineering aspects of clinical tasks. The informational aspect concerns the conditional probability that, for example, given activity in the motor areas of the brain in response to task instructions, a~patient is imagining wiggling toes. The engineering aspect concerns efficient activation of the relevant brain areas in a~patient under the task conditions. This distinction shows that the current alternative methods are not informationally problematic, but are structurally ``ill-formed.'' For instance, the toe-imagery task requires the capacity to comprehend syntactically complex sentences, which can be dissociated from minimal consciousness. I~propose a~misrepresentation task, which tests the capacity to misconceptualize lukewarm water as melting wax, as a~supplement to the current alternative methods. This task is as informationally reliable as these methods, but is structurally ``well-formed,'' as it does not rely methodologically on prerequisites such as language comprehension.
	}
	{post-comatose disorders of consciousness, Shannon's theory of information, minimal consciousness, mental action.}

\section{Introduction}
\lettrine[loversize=0.13,lines=2,lraise=-0.03,nindent=0em,findent=0.2pt]%
{M}{}inimally conscious post-comatose patients (henceforth, MCP patients) can have limited executive functions that allow for the patients to follow simple instructions or respond to certain stimulations. Signs of residual executive functions provide clinicians with strong evidence of eventual recovery of consciousness
%\label{ref:RNDc52VR2C0H1}(Naccache, 2018; Rohaut, Eliseyev and Claassen, 2019).
\parencites[][]{naccache_minimally_2018}[][]{rohaut_uncovering_2019}. %
 Thus, delayed recognition of such signs may lead to suboptimal clinical care 
%\label{ref:RND36iYhUl47e}(van Erp et al., 2019),
\parencite[van][]{van_erp_unexpected_2019}, %
 distorted prognostic figures for rehabilitation 
%\label{ref:RNDDiumYQqtvx}(Ansell, 1993),
\parencite[][]{ansell_slow--recover_1993}, %
 or ethical problems 
%\label{ref:RNDY4B7wdnTLX}(Peterson and Bayne, 2018; Noh, 2022).
\parencites[][]{peterson_post-comatose_2018}[][]{noh_behavioral_2022}. %
 Such signs, however, might not be captured by traditional behavioral assessments (e.g., eye tracking, speaking, etc.) because limited executive functions can be dissociated from the capacity to perform overt behaviors 
%\label{ref:RND1VSfdAw16s}(Teasdale and Jennett, 1974; Andrews et al., 1996).
\parencites[][]{teasdale_assessment_1974}[][]{andrews_misdiagnosis_1996}. %
 Although some traditional behavioral assessment methods can improve diagnostic accuracy 
%\label{ref:RNDkWoQFW7Rb7}(Schnakers et al., 2009),
\parencite[][]{schnakers_diagnostic_2009}, %
 differentiating MCP patients from patients in a~vegetative state remains challenging 
%\label{ref:RNDXmlWJMWjeY}(van Erp et al., 2015).
\parencite[van][]{van_erp_vegetative_2015}.%
